Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2024-09-28 manuscript.qmd
Added code to download processed data files

>>>>

if (processdata==1){
  if (!file.exists('local/processedE1.zip')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('processedE1.zip',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/processedE2.zip')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('processedE2.zip',osffiles$name)
osf_download(osffiles[fid,],path='local/')}

unzip('local/processedE1.zip',exdir='local')
unzip('local/processedE2.zip',exdir='local')
}
